---
title: "HW 1 Data Science"
format: html
editor: visual
---

## Data Science

Data science can be broadly characterized by:

-   Data access and import into a computing environment

-   tidying the data to ensure a consistent data standard - imputing missing values according to requirements - formatting date values according to requirements

-   transforming the data to ensure it can be analyzed appropriately

-   visualizing to gain intuition and check assumptions of the data

-   modeling to predict outcomes

-   communicating to show understanding of the problem and show results

Data Science can be further delineated into the functions and roles of:

-   Engineering

-   Analysis

-   Modeling and Inference

## Statisticians vs Data Scientists

Data Science is a rapidly evolving field that encompasses a breadth and depth of interdisciplinary expertise in numerous domains including statistics and machine learning, data architecture and engineering, systems architecture, computer science, and the soft skills to effectively engage upstream data stewards and downstream colleagues and interested parties.

In my experience and from a corporate perspective, statisticians often focus on the later stages of data science projects, such as modeling, analysis, visualization, and communication. They collaborate with others to define requirements early on, leaving data access, import, cleaning, and transformation to more technical roles. This highlights a practical distinction between these two skill sets in a corporate setting, because of the separation of concerns between job functions and access privileges to corporate data. In a more academic setting, even for my own personal projects surrounding NFL data, I find that as a burgeoning data scientist, I must be able to function across the entire data science lifecycle.

## My World View

I began my educational journey at NC State, graduating with a degree in Biochemistry. I didn't want to assume student debt so worked in the corporate world, came back and went through the computer programming certificate program, then spent my formative years as a SAS programmer for the pharmaceutical industry. I took a few graduate level stats courses with the goal of a Master's degree in an analytical role, and also started a family, so spent the next fifteen years working to provide. I am now back at NC State working towards my MBA, but I am also unemployed and want to find a role in data science/engineering while I work towards completion of the MBA. In pharma, there is a clear distinction between statisticians and data engineers—we refer to the data engineers as data managers, and there is a broad range of expertise among them, with most being more clerical in nature but some who understand how to work with a relational database and write code to tidy and transform data into the applicable data standards required by FDA for the purpose of submitting marketing applications for new drugs, biologics, and devices. I see myself as an interdisciplinary technologist. I can write, I can reason, and I can communicate to colleagues and leadership, but what I really want to get back to is writing and working towards building my Digital Tradesman practice, especially while I work towards my MBA.

## R Code

Density plot of Iris petal width

```{r}
y <- density(iris$Petal.Width)
```

Class of y

```{r}
class(y)
```

Type of y

```{r}
typeof(y)
```

Structure of y

```{r}
str(y)
```

Plot of y (density curve of Iris Petal Width)

```{r, echo=FALSE}
plot(y)
```
